Complexity Measures for Graphs

### 2012-11-05 P23WP1Q2Deliverable/src/deliverable.p23wp1q3.tex
...

\begin{tabular}{l | r r r r r r r r r r r r r r r }
  \hline
    & $N$ & $L$ & $W$ & $W_p$ & $D$ & $M$ & $C$ & $C_{WS}$ & $\alpha$ & $p_\alpha$ & $r$ & $d_B$ & $\bar{\kappa}$ & $\kappa_{\mbox{min}}$ & $\kappa_{\mbox{max}}$  \\
    \hline
 Internet & 22963 & 48436 & 75877.0 & 1.0 & & & & & & & & & & & \\   
 WWW & 325729 & 1497134 & & & & & & & & & & & & & \\
 Epinions & 75879 & 508837 & & & & & & & & & -0.01 & & & & \\ 
 Actors  & 383640 & 1229020 & & & & & & & & & & & & & \\
 E. Coli  & 2859 & 6890 & 2859 & 1.0 & 18 & 4.70 & 0 & 0 & & & -0.16 & & & & \\
 C. Elegans  & 297 & 2345 & 297 & 1.0 & 5 & 2.45 & 0.18 & 0.29 & & & -0.15 & -4.5 & 0.39 & 0.38 & 0.39 \\
 IAFB  & 8318 & 61255 & 8318 & 1.0 & & & & & & & -0.26 & & 0.025 & &  \\ 
 \hline

>>>>

\begin{tabular}{l | r r r r r r r r r r r r r r r }
  \hline
    & $N$ & $L$ & $W$ & $W_p$ & $D$ & $M$ & $C$ & $C_{WS}$ & $\alpha$ & $p_\alpha$ & $r$ & $d_B$ & $\bar{\kappa}$ & $\kappa_{\mbox{min}}$ & $\kappa_{\mbox{max}}$  \\
    \hline
 Internet & 22963 & 48436 & 75877.0 & 1.0 & & & & & 2.1 & 0.5 & & & & & \\   
 WWW & 325729 & 1497134 & & & & & & & \color{gray} 2.5 & 0.0 & & & & & \\
 Epinions & 75879 & 508837 & & & & & & & 3.8 & 0.6 & -0.01 & & & & \\ 
 Actors  & 383640 & 1229020 & & & & & & & \color{gray}2.5 & 0.0 & -0.12 & & & & \\
 E. Coli  & 2859 & 6890 & 2859 & 1.0 & 18 & 4.70 & 0 & 0 & \color{gray} 2.3 & 0.04 & -0.16 & & & & \\
 C. Elegans  & 297 & 2345 & 297 & 1.0 & 5 & 2.45 & 0.18 & 0.29 & 3.3 & 0.33 & -0.15 & -4.5 & 0.39 & 0.38 & 0.39 \\
 IAFB  & 8318 & 61255 & 8318 & 1.0 & & & & & \color{gray} 2.2 & 0.0 & -0.26 & & 0.025 & &  \\ 
 \hline
